---
title: "Rbutchland"
author: "Butch Landingin"
date: "Tuesday, 25 August, 2015"
output: html_document
---

Rbutchland: A suite of useful and (hopefully) reusable routines
=====================

This R package contains a suite of useful routines that I hope
to turn into a reusable package. Right now, it doesn't contain
much. My goal is to build a suite of useful routines 
for data exploration and manipulation.

Installation and Documentation
------------

The Rbutchland package is available on github and can be installed using
[devtools](https://github.com/hadley/devtools):

```
library(devtools)
install_github("butchland/Rbutchland")
```
```{r results='hide',echo=FALSE}
library(Rbutchland)
```


Dataframe stats
-----------------

This package provides some simple methods for extracting information
about a dataframe

* `df_boxstat`: constructs a data frame that summarizes the dataframes's
size (nrows and ncols)

```{r}
df_boxstat(mtcars)
```
* `df_columnstat`: constructs a data frame that summarizes the dataframes's
columns (column names, type and count(NAs))
```{r}
df <- data.frame(x=c(1,2,3),y=c("a","b",NA),z=c("a","b",NA))
df$z = as.character(df$z)
df_columnstat(df)
```

